---
title: "Introduction to R using Stencila"
author: 
  - Francois Michonneau
  - Auriel Fournier
  - Ana Costa Conrado
  - Brian Seok
  - Nokome Bentley
  - Aleksandra Pawlik
output: html_document
---


## Introduction to R using Stencila

This training material is based on [Data Carpentry](http://www.datacarpentry.org/) lesson on [Introduction to R](http://www.datacarpentry.org/R-ecology-lesson). Originally this document is written in 
RMarkdown but if you are not familiar with that format (Rmd), you can still open and edit this document using Stencila. 


## Starting with R

Let's start with a simple expression:

```{r}
3+2
```

To do useful and interesting things, we need to assign values to objects. To create an object, we need to give it a name followed by the assignment operator <-, and the value we want to give it:

```{r}
weight_kg <- 55
```

<- is the assignment operator. It assigns values on the right to objects on the left. So, after executing  x <- 3, the value of x is 3. The arrow can be read as 3 goes into x. For historical reasons, you can also use = for assignments, but not in every context. Because of the slight differences in syntax, it is good practice to always use <- for assignments.

Now that R has weight_kg in memory, we can do arithmetic with it. For instance, we may want to convert this weight into pounds (weight in pounds is 2.2 times the weight in kg):

```{r}
2.2 * weight_kg
```



## The data

We are using a subset (1000 records) of the training sample dataset used for the aforementioned Data Carpentry R lesson.

First, let's get that dataset downloaded (if you are in Stencila Hub, it will be downloaded to Stencila Hub): 


```{r}
setwd("path")
```

```{r}
download.file('http://storage.googleapis.com/stencila-hubstatic-test/surveys_complete.csv', 'surveys_complete.csv')
```

```{r}
surveys_complete <- read.csv('surveys_complete.csv')
```


```{r}
summary(surveys_complete)
```
Let's do some analysis

```{r}
install.packages("tidyverse")
```

```{r}
library(tidyverse)
```

```{r}
filter(surveys_complete, year ==  1998)
```


```{r}
select(surveys_complete, species_id, sex)
```


```{r}
 surveys_complete %>% 
  filter(year == 1998) %>%
  select(species_id, sex)
```


```{r}
 surveys_complete %>% 
  filter(year > 1998) %>%
  select(species_id, sex, year)
```

```{r}
colnames(surveys_complete)
```


```{r}
select(surveys_complete, weight)
```

How many females were caught after 1995 and what was their species ID - and what was their weight in kg?

sex == "F"

```{r}
surveys_complete %>% 
  filter(sex == "F") %>%
  filter(year > 1995) %>%
  mutate(weight_kg = weight/1000) %>%
  select(species_id, weight_kg)
```

```{r}
females_1995 <- surveys_complete %>% 
  filter(sex == "F") %>%
  filter(year > 1995) %>%
  mutate(weight_kg = weight/1000) %>%
  select(species_id, weight_kg)
```

```{r}
write.csv(females_1995, file="females_1995.csv", row.names = FALSE)
```

```{r}
write.csv(surveys_complete %>%
  group_by(species_id, sex) %>%
  summarize(mean_weight = round(mean(weight), 1 ), min_weight = min(weight), max_weight = max(weight)  ) %>%
  arrange(desc(mean_weight)), file="weights.csv")
```


```{r}
surveys_complete <- surveys_complete %>%
   mutate(weight_kg = weight / 1000)
```
